\speculake: Hiding Malware in Speculative Execution

### 2018-05-08 paper/discussion.tex
add discussion on approximate computing

\subsubsection{Alternative Applications}
We have proposed the \speculake model as a new malware threat, however, this model
of hidden computation applies more broadly. As of now there are no ways of 
debugging speculative computation meaning that the computation done there is effectively
isolated as with trusted execution environments. The security provided by the obfuscated 
key schedule makes \speculake useful in the domains of Digital Rights Management (DRM)
and whitebox cryptography, and apprimate computing fields. 
%% Approximate Computing

>>>>

\subsubsection{Alternative Applications}
We have proposed the \speculake model as a new malware threat, however, this
model of hidden computation applies more broadly. As of now there are no ways of
debugging speculative computation meaning that the computation done there is
effectively isolated as with trusted execution environments. The security
provided by the obfuscated key schedule makes \speculake useful in the domains
of Digital Rights Management (DRM) and whitebox cryptography, and approximate
computing fields. 
%% Approximate Computing

Approximate Computing prioritizes the computation of quick results that are
potentially incorrect. This form of computation often leverages some type of
machine learning to determine how well individual results fit with a crowd of
approximately computed results. As mentioned in Section~\ref{subsec:impl-turing}
occasionally values necessary for computation in the speculative world are not
in cache and thus must be speculated themselves. In this situation error
correcting codes are useless given that the mistake is not a mutation of the
correct input, but rather a guess at what the input might be. The mechanisms
used in approximate computing may be beneficial here, allowing computation to
run speculatively and results be analyzed after the computation to determine how
results fit, with the understanding that these results may not be accurate.
